How to obtain the redshift distribution from probabilistic redshift estimates

### 2020-07-01 research/paper/draft.tex
finalized!

\usepackage{tikz}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{hyperref}
%\usepackage{graphicx}
%\usepackage{lineno}

\usetikzlibrary{shapes.geometric, arrows}
\usetikzlibrary{fit}

\tikzstyle{hyper} = [circle, text centered, draw=black]
\tikzstyle{param} = [circle, text centered, draw=black]
\tikzstyle{data} = [circle, text centered, draw=black, line width=2pt]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

@@

% how people get n(z) from photo-z PDFs
Though it is traditional to estimate \nz\ from \pz\ point estimates \citep{abruzzo_impact_2019}, it has become more common to use \pzpdf s directly to calculate the conceptually simple but mathematically inconsistent \citep{hogg_data_2012} \textit{stacked estimator} $\hat{n}(z)$ of the redshift density function \citep{lima_estimating_2008}
\begin{align}
\label{eqn:stack}
\hat{n}(z) &= \frac{1}{J} \sum_{j = 0}^{J} \pr{z}_{j}
\end{align}
for a sample of $J$ galaxies $j$, or, equivalently, the redshift distribution function $\hat{N}(z) = J \hat{n}(z)$, by effectively averaging the \pzpdf s.
This summation procedure has been used extensively in cosmological analyses with photometric galaxy samples \citep{mandelbaum_precision_2008, benjamin_cfhtlens_2013, kelly_weighing_2014}.
%\aim{\dots}
%\aim{TODO: Continue adding equations/citations for the use of \Nz\ in cosmology.}

@@

In Section~\ref{sec:meth}, we present the \Chippr\ model and \chippr\ implementation for characterizing the full posterior probability landscape of \Nz\ using \pzpdf s. 
In Section~\ref{sec:alldata}, we describe the experimental design for testing the fully probabilistic approach to mock and real datasets, the results of which are found in Section~\ref{sec:results}.
In Section~\ref{sec:results}, we stress-test the \Chippr\ model against stacking and its other competitors.
% in the context of cosmology.

\section{Method}
\label{sec:meth}

Consider a survey of $J$ galaxies $j$, each with photometric data $\data_{j}$; thus the entire survey over some solid angle produces the ensemble of photometric magnitudes (or colors) and their associated observational errors $\{\data_{j}\}$.  
Each galaxy $j$ has a redshift $z_{j}$ that we would like to learn; redshift is a parameter in this case.  
The distribution of the ensemble of redshifts $\{z_{j}\}$ may be described by the hyperparameters defining the redshift distribution function \nz\ that we would like to quantify.  
This situation may be considered to be a probabilistic generative model, illustrated by the directed acyclic graph of \Fig{fig:pgm}.

The redshift distribution function \nz\ is the number of galaxies per unit redshift, effectively defining the evolution in the number of galaxies convolved with the selection function of the sample \citep{menard_clustering-based_2013}.  
In the following sections, we present and compare methods for estimating \nz\ from \pzpdf s.  
\Sect{sec:prob} contains the mathematical derivation of a probabilistic model for $n(z)$ dependent on photo-$z$ probability distribution functions, and \Sect{sec:sheldon} contrasts the probabilistic model with alternative methods.

@@

We begin by reframing the redshift distribution \nz\ from a probabilistic perspective.
Here we define a redshift density \nz\ as the normalized probability density
\begin{equation}
\label{eqn:nz}
\int_{-\infty}^{\infty}\ n(z)\ dz\ \equiv\ \frac{1}{J}\ \int_{-\infty}^{\infty}\ \sum_{j=1}^{J}\ \delta(z_{j},\ z)\ dz = 1
\end{equation}
of finding a galaxy $j$ in a catalog of $J$ galaxies having a redshift $z$.
We believe that galaxy redshifts are indeed drawn from \nz, making it a probability density over redshift; this fact can also be confirmed by dimensional analysis of \Eq{eqn:nz}, as suggested in \citet{hogg_data_2012}.

We may without loss of generality impose a parameterization
\begin{equation}
\label{eqn:fz}
f(z; \ndphi)\ \equiv\ n(z)
\end{equation}
in terms of some parameter vector $\ndphi$.
At this point, the parameter vector is quite general and may represent coefficients in a high-order polynomial as a function of redshift, a set of means and variances defining Gaussians that sum to the desired distribution, a set of histogram heights that describe a binned version of the redshift distribution function, etc.
Upon doing so, we may rewrite \Eq{eqn:fz} as 
\begin{equation}
\label{eqn:pz}
z_{j}\ \sim\ \pr{z \gvn \ndphi}\ \equiv\ f(z; \ndphi),
\end{equation}
% \aim{explain "is drawn from"}
a probability density over redshift conditioned on the parameters $\ndphi$ specifying \nz.
Note that $z_{j}$ does not depend on the redshift $z_{j'}$ of some other galaxy $j' \neq j$, a statement of the causal independence of galaxy redshifts from one another.

@@

When we constrain the redshift of a galaxy using its observed photometric data $\data_{j}$, we are effectively estimating a posterior $\pr{z \gvn \data_{j}}$, the probability of an unknown quantity conditioned on the quantity we have in hand, i.e the photometric data.
This posterior is effectively a marginalization with respect to redshift at a given value of $\data = \data_{j}$ of the \textit{empirical frequency distribution} $\pr{z, \data \gvn \ndphi^{\dagger}}$, the joint probability density corresponding to the true redshift distribution parameterized by $\ndphi^{\dagger}$, which exists in nature but need not be known.
\que{Propagate new $\pr{z, \data \gvn \ndphi^{\dagger}}$ notation through appendix?}

@@

\subsubsection{Model Limitations}
\label{sec:limitations}

@@

@@

Though there are plans for future expansion to more flexible parameterizations, the current version of \chippr\ uses a log-space piecewise constant parameterization
\begin{equation}
\label{eqn:logstepfunc}
f(z; \ndphi) = \exp[\phi^{k}]\ \mathrm{if}\ z^{k} < z < z^{k+1}
\end{equation}
for \nz\ and every \pzpdf, satisfying
\begin{equation}
\label{eqn:logstepfuncnorm}
\sum_{k=1}^{K} \exp[\phi^{k}] \delta z^{k} = 1
\end{equation}
with $K$ bins of width $\delta z^{1}, \dots, \delta z^{K}$ defined by endpoints $z^{0}, \dots, z^{K}$.
%\aim{Maybe include an equation for a general piecewise constant function here (which is currently in \Chap{qp})?}
Thus each $\pr{z \gvn \data_{j}} = f(z; \ndphi_{j})$ has parameters $\ndphi_{j}$ that are defined in the same basis as those of \nz.
To infer the full log-posterior distribution $\ln[\pr{\ndphi \gvn \{\data_{j}\}}]$, one must provide a plaintext file with $K+1$ redshift bin endpoints $\{z_{k}\}$, the parameters $\ndphi^{*}$ of the implicit log-prior, and the parameters $\{\ndphi_{j}\}$ of the log-posteriors $\ln[\pr{z \gvn \data_{j}, \ndphi^{*})}$.

@@

\subsection{Alternative approaches for comparison}
\label{sec:sheldon}

@@

A final estimator of the hyperparameters is the maximum marginalized likelihood estimator (MMLE), the value of $\ndphi$ maximizing the log posterior given by \Eq{eqn:final} using any optimization code.  
To compare with sampling, the MMLE also depends on the choice of the hyperprior distribution, and it does not produce a full posterior probability distribution over the parameters of interest, only point estimators.  
It must be noted that computation of the maximum marginalized likelihood estimator may be unstable depending on the strengths and weaknesses of the optimizer.  
In general, derivatives will not be available for the full posterior distribution, restricting optimization methods used.
%\begin{equation}
%\label{eq:mmle}
%\ln[p(\{\vec{d}_{j}\}|\vec{\theta})] \propto -\int\ f_{\vec{\theta}}(z)\ 
%dz+\sum_{j=1}^{J}\ln\left[\int\ 
%\exp\left[\ln[p(z_{j}|\vec{d}_{j},\vec{\theta}^{*})]+\ln[f_{\vec{\theta}}(z)]-\l
%n[f_{\vec{\theta}^{*}}(z)]\right]\ dz\right],
%\end{equation}
%accessible with any optimization code.

\subsection{Performance metrics}
\label{sec:diag}

@@

In simulated cases where the true parameter values are known, we calculate the Kullback-Leibler divergence (KLD), given by 
\begin{equation}
\label{eqn:kl}
KL_{',\ddagger} = \integral{\pr{z \gvn \ndphi'} \ln \left[ \frac{\pr{z \gvn \ndphi'}}{\pr{z \gvn \ndphi^{\dagger}}} \right]}{z} ,
\end{equation}
which measures a distance from parameter values $\ndphi'$ to true parameter values $\ndphi^{\dagger}$, which is invariant under changes of variables.  
We note that $KL_{',\dagger} \neq KL_{\dagger,'}$ and is only interpretable when there is a notion that $\ndphi^{\dagger}$ is closer to the truth than $\ndphi'$.
The KLD is explored in detail in the Appendix to \citet{malz_approximating_2018}.
In simulated tests, $\ndphi^{\dagger}$ is the true value and $\ndphi'$ is that produced by one of the methods in question.

@@

@@

\begin{figure}
	\begin{center}
%		\includegraphics[width=0.32\textwidth]{figures/chippr/thesis_hivarsig-mega_scatter.png}
%		\includegraphics[width=0.32\textwidth]{figures/chippr/single_uout-mega_scatter.png}
%		\includegraphics[width=0.32\textwidth]{figures/chippr/thesis_neghivarbias-mega_scatter.png}
		\includegraphics[width=0.45\textwidth]{figures/chippr/single_lsst-mega_scatter.png}
		\caption{
			The joint probability space of true and estimated redshift for the three concerning \pz\ systematics at the level of the \lsst\ requirements: intrinsic scatter, uniformly distributed catastrophic outliers, and bias.
			The main panel shows samples (black points) in the space of mock data and redshift, akin to the standard scatterplots of true and estimated redshift, the $z_{\mathrm{spec}} = z_{\mathrm{phot}}$ diagonal (gray line), and posterior probabilities evaluated at the given estimated redshift (colored step functions).
			The insets show marginal histograms (light gray) in each dimension, that can be compared with the true \nz\ used to make the figure (black) to see the effect of these systematics, as well as the implicit prior (dark gray).
			\aim{TODO: Include slice further up so we can see outliers.
				Label panel.}
			}
		\label{fig:mega_scatter}
	\end{center}
\end{figure}

@@

%An example of such samples from the prior are shown in \Fig{fig:prior}.
%
%\begin{figure}
%%	\includegraphics[width=0.5\textwidth]{figures/chippr/null_priorsamps.pdf}
%	\caption{\aim{I need to remake this one because it uses the wrong notation and I stopped making it automatically a while ago.}
%		Samples (colored lines) of $\pr{z \gvn \ndphi}$ where each $\ndphi$ is drawn from the hyperprior distribution $\pr{\ndphi}$ given in \Eq{eqn:priorcov}.}
%	\figlabel{fig:prior}
%\end{figure}
%\que{Should I add back the figure of prior samples?}

@@

\que{Tests including all three canonical effects at the tolerance levels of \lsst\ were once in \Sect{sec:results} but Hogg requested the section be removed.
	Include results of all 3 canonical effects combined at LSST levels here?}

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/single_varsigmas-mega_scatter.png}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_hivarsig-mega_scatter.png}
	\caption{
		Examples of mock \pzpdf s generated with intrinsic scatter at the \lsst\ requirements (left) and twice the \lsst\ requirements (right), including samples from the probability space of true and observed redshift (black points), \pzpdf s (colored step functions), and the true redshifts of the example \pzpdf s (colored vertical lines).
		A histogram (light gray) of points in each dimension is shown in the respective inset, with the true redshift distribution (black) and implicit prior (dark gray).
		\aim{TODO: Label panels.
		Show the mean redshift for each estimator.}
	}
	\label{fig:pzs-scatter}
	\end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.45\textwidth]{figures/chippr/single_varsigmas_log_estimators.png}
		\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_hivarsig_log_estimators.png}
	\caption{
		The results of \Chippr\ (samples in light blue and optimization in dark blue) and the alternative approaches (the stacked estimator in red and the histogram of modes in yellow) on \pzpdf s with intrinsic scatter of the \lsst\ requirements (left) and twice that (right), with the true redshift density (black curve) and implicit prior (gray curve).
		\Chippr\ is robust to intrinsic scatter, but the alternatives suffer from overly broad \nz\ estimates that worsen with increasing intrinsic scatter.
		\aim{TODO: Label panels.
		Show the mean redshift for each estimator.}
	}
	\label{fig:results-scatter}
	\end{center}
\end{figure*}

@@

\begin{figure}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/single_uout-mega_scatter.png}\\
	\includegraphics[width=0.45\textwidth]{figures/chippr/single_uout_log_estimators.png}
	\caption{
		Top: Examples of \pzpdf s with a uniformly distributed catastrophic outlier population at the level of the \lsst\ requirements, including samples from the probability space of true and observed redshift (black points), \pzpdf s (colored step functions), and the true redshifts of the example \pzpdf s (colored vertical lines), with marginal histograms (light gray) for each dimension with the true redshift distribution (black) and implicit prior (dark gray) in the insets.
		\aim{TODO: Include slice further up.
		Label panels.}
		Bottom: The results of \Chippr\ (samples in light blue, optimization in dark blue) and the alternative approaches (the stacked estimator in red, the histogram of modes in yellow) on \pzpdf s with uniformly distributed catastrophic outliers, with the true redshift density (black curve) and implicit prior (gray curve).
		\aim{TODO: Label panels.
		Show the mean redshift for each estimator.}
		The presence of the catastrophic outlier population broadens the histogram of modes and stacked estimator of the redshift distribution, but the result of \Chippr\ is unbiased.
	}
	\label{fig:uniform-outliers}
	\end{center}
\end{figure}

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_eout-mega_scatter.png}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_rout-mega_scatter.png}
	\caption{
		Examples of \pzpdf s with a catastrophic outlier population like that seen in template-fitting \pzpdf\ codes (left) and machine learning \pzpdf\ codes (right), including samples from the probability space of true and observed redshift (black points), \pzpdf s (colored step functions), and the true redshifts of the example \pzpdf s (colored vertical lines), with marginal histograms (light gray) for each dimension with the true redshift distribution (black) and implicit prior (dark gray) in the insets.
		\aim{TODO: Label panels.
		Include slices higher up.}		
	}
	\label{fig:nonuniform-outliers-data}
	\end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_eout_log_estimators.png}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_rout_log_estimators.png}
	\caption{
		The results of \Chippr\ (samples in light blue and optimization in dark blue) and the alternative approaches (the stacked estimator in red, the histogram of modes in yellow) on \pzpdf s with catastrophic outliers like those seen in template-fitting \pzpdf\ codes (left) and machine learning \pzpdf\ codes (right) to the \lsst\ requirements, with the true redshift density (black curve) and implicit prior (gray curve).
		Though the histogram of modes is most sensitive to a catastrophic outlier population, the stacked estimator also overestimates \nz\ under (machine learning-like outliers) and beyond (template fitting-like outliers).
		\aim{TODO: Label panels.
		Show the mean redshift for each estimator.}
	}
	\label{fig:nonuniform-outliers-results}
	\end{center}
\end{figure*}

@@

Systematic bias in \pz\ point estimates, is a concern for \lsst's cosmology results, for the same reasons explored in \citet{hoyle_dark_2018}.
\aim{TODO: Cite a KiDS and/or HSC paper using $\Delta_{z}$, too.}
This form of bias is typically summarized by a shift parameter $\Delta_{z} = (\langle \pr{z \gvn \hat{\ndphi}} \rangle - \langle \pr{z \gvn \ndphi^{\dagger}} \rangle)$ representing a difference between the first moment of the estimated redshift density function and that of the true redshift density function.
To distinguish other aforementioned manifestations of bias from this common form of bias, we refer to $\Delta_{z}$ as the \textit{canonical bias}.

@@

@@

%%Though redshift tomography is non-physical, as redshift is a continuous random variable, and binning in estimated redshift introduces poorly understood systematic error, we perform this analysis as an example of how it affects the current standard in how cosmological parameters are constrained by galaxy surveys, rather than how we think they ought to be constrained.
%%\aim{Don't introduce anti-tomography rant here, kind of controversial and should be explored where it has its own space.}

@@

%%\aim{TODO: Ask Elisabeth how to get the bias here.}

@@

%\aim{TODO: Break up conclusion into subsections of \Sect{sec:alldata}/\Sect{sec:results}.}
\aim{TODO: Add subsection on support; must have support everywhere in z, data in observation/universe and prior, and support is not guaranteed (cite qp for defining support)}

@@

\aim{TODO: point out that Fig 1 is uglier than 4, 5, 7, 8, 10, 11; these tests are simplistic, reality is more complex, but because \Chippr is provably correct, it can handle complexity of the real thing if p(z) is correct and captures complexity}

@@

In this paper, we work exclusively with log-probabilities.  
What we wish to estimate is then the full log-posterior probability distribution (hereafter the full log-posterior) of the hyperparameters $\ndphi$ given the catalog of photometry $\{\data_{j}\}$.

@@

>>>>

\usepackage{tikz}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{hyperref}
%\usepackage{graphicx}
%\usepackage{lineno}
\usepackage[percent]{overpic}
\usepackage{float}
\usepackage{wrapfig}

%\usetikzlibrary{shapes.geometric, arrows}
%\usetikzlibrary{fit}
%
%\tikzstyle{hyper} = [circle, text centered, draw=black]
%\tikzstyle{param} = [circle, text centered, draw=black]
%\tikzstyle{data} = [circle, text centered, draw=black, line width=2pt]
%\tikzstyle{arrow} = [thick,->,>=stealth]

@@

%\aim{TODO: Add test case panel labels to all figs of \chippr\ sims/outputs.  Take higher-z samples in mock \pzpdf\ plots relative to outlier populations.  Include $\bar{z}$ in results plots.}

@@

% how people get n(z) from photo-z PDFs
Though it is traditional to estimate \nz\ from \pz\ point estimates \citep{abruzzo_impact_2019}, it has become more common to use \pzpdf s directly to calculate the conceptually simple but mathematically inconsistent \citep{hogg_data_2012} \textit{stacked estimator} $\hat{n}(z)$ of the redshift density function \citep{lima_estimating_2008}
\begin{align}
\label{eqn:stack}
\hat{n}(z) &= \frac{1}{J} \sum_{j = 0}^{J} \pr{z}_{j}
\end{align}
for a sample of $J$ galaxies $j$, or, equivalently, the redshift distribution function $\hat{N}(z) = J \hat{n}(z)$, by effectively averaging the \pzpdf s.
This summation procedure has been used extensively in cosmological analyses with photometric galaxy samples \citep{mandelbaum_precision_2008, benjamin_cfhtlens_2013, kelly_weighing_2014}.
%\aim{TODO: Continue adding equations/citations for the use of \Nz\ in cosmology.}

@@

In Section~\ref{sec:meth}, we present the \Chippr\ model for characterizing the full posterior probability landscape of \Nz\ using \pzpdf s. 
In Section~\ref{sec:application}, we present the \chippr\ implementation of the \Chippr\ model and the experimental set up by which we validate it, including the forward modeling of mock \pzpdf s.
In Section~\ref{sec:alldata}, we present a number of informative test cases and compare the results of \chippr\ with alternative approaches.
In Section~\ref{sec:results}, we stress-test the \Chippr\ model under nontraditional conditions.
% in the context of cosmology.
Finally, in Section~\ref{sec:con}, we make recommendations for future research involving \nz\ estimation.

\section{Model}
\label{sec:meth}

Consider a survey of $J$ galaxies $j$, each with photometric data $\data_{j}$; 
thus the entire survey over some solid angle produces the ensemble of photometric magnitudes (or colors) and their associated observational errors $\{\data_{j}\}$.  
Each galaxy $j$ has a redshift parameter $z_{j}$ that we would like to learn.  
The distribution of the ensemble of redshift parameters $\{z_{j}\}$ may be described by the hyperparameters defining the redshift distribution function \nz\ that we would like to quantify.
The redshift distribution function \nz\ is the number of galaxies per unit redshift, effectively defining the evolution in the number of galaxies convolved with the selection function of the sample \citep{menard_clustering-based_2013}.

In \Sect{sec:forward}, we establish a forward model encapsulating the causal relationship between \nz\ and photometry $\data$.  
In \Sect{sec:prob}, we present the directed acyclic graph of this probabilistic generative model and interpret the corresponding mathematical expression, whose full derivation may be found in the Appendix.
In \Sect{sec:limitations}, we summarize the necessary assumptions of the model.

%\aim{TODO: check for consistent notation of \pzip s vs. \pzpdf s.}

@@

We begin by reframing the redshift distribution \nz\ from a probabilistic perspective.
Here we define a redshift density \nz\ as the normalized probability density
\begin{equation}
\label{eqn:nz}
\int_{-\infty}^{\infty}\ n(z)\ dz\ \equiv\ \frac{1}{J}\ \int_{-\infty}^{\infty}\ \sum_{j=1}^{J}\ \delta(z_{j},\ z)\ dz = 1
\end{equation}
of finding a galaxy $j$ in a catalog of $J$ galaxies having a redshift $z$.
We believe that galaxy redshifts are indeed sampled, or drawn, from \nz, making it a probability density over redshift; this fact can also be confirmed by dimensional analysis of \Eq{eqn:nz}, as suggested in \citet{hogg_data_2012}.

We may without loss of generality impose a parameterization
\begin{equation}
\label{eqn:fz}
f(z; \ndphi)\ \equiv\ n(z)
\end{equation}
in terms of some parameter vector $\ndphi$.
At this point, the parameter vector is quite general and may represent coefficients in a high-order polynomial as a function of redshift, a set of means and variances defining Gaussians that sum to the desired distribution, a set of histogram heights that describe a binned version of the redshift distribution function, etc.
Upon doing so, we may rewrite \Eq{eqn:fz} as 
\begin{equation}
\label{eqn:pz}
z_{j}\ \sim\ \pr{z \gvn \ndphi}\ \equiv\ f(z; \ndphi),
\end{equation}
a probability density over redshift conditioned on the parameters $\ndphi$ specifying \nz.
Note that $z_{j}$ does not depend on the redshift $z_{j'}$ of some other galaxy $j' \neq j$, a statement of the causal independence of galaxy redshifts from one another.

@@

When we constrain the redshift of a galaxy using its observed photometric data $\data_{j}$, we are effectively estimating a posterior $\pr{z \gvn \data_{j}}$, the probability of an unknown quantity conditioned on the quantity we have in hand, i.e the photometric data.
This posterior is effectively a marginalization with respect to redshift at a given value of $\data = \data_{j}$ of the \textit{empirical frequency distribution} $\pr{z, \data \gvn \ndphi^{\dagger}}$, the joint probability density corresponding to the true redshift distribution parameterized by $\ndphi^{\dagger}$, which exists in nature but need not be known.
%\que{Propagate new $\pr{z, \data \gvn \ndphi^{\dagger}}$ notation through appendix?}

@@

\subsection{Model Limitations}
\label{sec:limitations}

@@

Furthermore, in Section~\ref{sec:prob}, we have made an assumption of \textit{support}, meaning the model $\pr{z, \data \gvn \ndphi}$ has mutual coverage with the parameter values that real galaxies can take.  
In other words, any probability distribution over the $(z, \data)$ space must be nonzero where real galaxies can exist. 
Additionally, the hyperprior $\pr{\ndphi}$ must be nonzero at the hyperparameters $\ndphi^{\dagger}$ of the true redshift density function \nz.
This assumption cannot be violated under the experimental design of Section~\ref{sec:forward}, but it is not generically guaranteed when performing inference on real data;
thus the chosen $\pr{z, \data \gvn \ndphi^{*}}$ and $\pr{\ndphi}$ must be sufficiently general as to not rule out plausible areas of parameter space.

\section{Methods \& Data}
\label{sec:application}

Here we describe the method by which we demonstrate the \Chippr\ model.
In \Sect{sec:exp}, we outline the implementation of the \chippr\ code.
In \Sect{sec:sheldon}, we introduce the alternative \nz\ estimators against which \Chippr\ is compared.
In \Sect{sec:diag}, we present the quantitative metrics by which 
In \Sect{sec:mock}, we outline the procedure for emulating mock \pzip s.

@@

Though there are plans for future expansion to more flexible parameterizations, the current version of \chippr\ uses a log-space piecewise constant parameterization
\begin{equation}
\label{eqn:logstepfunc}
f(z; \ndphi) = \exp[\phi^{k}]\ \mathrm{if}\ z^{k} < z < z^{k+1}
\end{equation}
for \nz\ and every \pzpdf, satisfying
\begin{equation}
\label{eqn:logstepfuncnorm}
\sum_{k=1}^{K} \exp[\phi^{k}] \delta z^{k} = 1
\end{equation}
with $K$ bins of width $\delta z^{1}, \dots, \delta z^{K}$ defined by endpoints $z^{0}, \dots, z^{K}$.
Thus each $\pr{z \gvn \data_{j}} = f(z; \ndphi_{j})$ has parameters $\ndphi_{j}$ that are defined in the same basis as those of \nz.
To infer the full log-posterior distribution $\ln[\pr{\ndphi \gvn \{\data_{j}\}}]$, one must provide a plaintext file with $K+1$ redshift bin endpoints $\{z_{k}\}$, the parameters $\ndphi^{*}$ of the implicit log-prior, and the parameters $\{\ndphi_{j}\}$ of the log-posteriors $\ln[\pr{z \gvn \data_{j}, \ndphi^{*})}$.

@@

\subsubsection{Alternative approaches for comparison}
\label{sec:sheldon}

@@

A final estimator of the hyperparameters is the maximum marginalized likelihood estimator (MMLE), the value of $\ndphi$ maximizing the log posterior given by \Eq{eqn:final} using any optimization code. 
The MMLE can be obtained in substantially less time than enough samples to characterize the full log-posterior distribution of \nz.
However, the MMLE yields only a point estimate of \nz\ rather than characterizing the full log-posterior on $\ndphi$, and it does not escape the dependence on the choice of hyperprior distribution.  
Furthermore, derivatives will not in general be available for the full posterior distribution, restricting optimization methods used, and, as is true for any optimization code, there is a risk of numerical instability.
%\begin{equation}
%\label{eq:mmle}
%\ln[p(\{\vec{d}_{j}\}|\vec{\theta})] \propto -\int\ f_{\vec{\theta}}(z)\ 
%dz+\sum_{j=1}^{J}\ln\left[\int\ 
%\exp\left[\ln[p(z_{j}|\vec{d}_{j},\vec{\theta}^{*})]+\ln[f_{\vec{\theta}}(z)]-\l
%n[f_{\vec{\theta}^{*}}(z)]\right]\ dz\right],
%\end{equation}
%accessible with any optimization code.

\subsubsection{Performance metrics}
\label{sec:diag}

@@

In simulated cases where the true parameter values are known, we calculate the Kullback-Leibler divergence (KLD), given by 
\begin{equation}
\label{eqn:kl}
KL_{\ndphi,\ndphi^{\ddagger}} = \integral{\pr{z \gvn \ndphi} \ln \left[ \frac{\pr{z \gvn \ndphi}}{\pr{z \gvn \ndphi^{\dagger}}} \right]}{z} ,
\end{equation}
which measures a distance from parameter values $\ndphi$ to true parameter values $\ndphi^{\dagger}$.  
The KLD is a measure of the information loss, in units of nats, due to using $\ndphi$ to approximate the true $\ndphi^{\dagger}$ when it is known.
A detailed exploration of the KLD may be found in the Appendix to \citet{malz_approximating_2018}.
%We note that $KL_{\ndphi,\ndphi^{\ddagger}} \neq KL_{\ndphi^{\ddagger},\ndphi}$ and is only interpretable when there is a notion that $\ndphi^{\dagger}$ is closer to the truth than $\ndphi$.
%In simulated tests, $\ndphi^{\dagger}$ is the true value and $\ndphi'$ is that produced by one of the methods in question.

@@

\subsection{Validation on mock data}
\label{sec:mock}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.45\textwidth]{figures/chippr/single_lsst-mega_scatter.png}
		\caption{
			The joint probability space of true and estimated redshift for the three concerning \pz\ systematics at the level of the \lsst\ requirements: intrinsic scatter, uniformly distributed catastrophic outliers, and bias.
			The main panel shows samples (black points) in the space of mock data and redshift, akin to the standard scatterplots of true and estimated redshift, the $z_{\mathrm{spec}} = z_{\mathrm{phot}}$ diagonal (gray line), and posterior probabilities evaluated at the given estimated redshift (colored step functions).
			The insets show marginal histograms (light gray) in each dimension, that can be compared with the true \nz\ used to make the figure (black) to see the effect of these systematics, as well as the implicit prior (dark gray).
%			\aim{TODO: Include slice further up so we can see outliers.
%				Label panel.}
		}
		\label{fig:mega_scatter}
	\end{center}
\end{figure}

@@

%An example of such samples from the prior are shown in \Fig{fig:prior}.
%\que{Should I add back the figure of prior samples?}

@@

Here, we compare the results of the \Chippr\ methodology with those of established \nz\ estimators under the three traditional measures of \pz\ uncertainty one at a time:
\Sect{sec:scatter} concerns the redshift-dependent intrinsic scatter, \Sect{sec:outliers} concerns realistically complex catastrophic outlier populations, and \Sect{sec:bias} concerns the canonical bias in the mean redshift.

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/single_varsigmas-mega_scatter.png}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_hivarsig-mega_scatter.png}
	\caption{
		Examples of mock \pzpdf s generated with intrinsic scatter at the \lsst\ requirements (left) and twice the \lsst\ requirements (right), including samples from the probability space of true and observed redshift (black points), \pzpdf s (colored step functions), and the true redshifts of the example \pzpdf s (colored vertical lines).
		A histogram (light gray) of points in each dimension is shown in the respective inset, with the true redshift distribution (black) and implicit prior (dark gray).
%		\aim{TODO: Label panels.
%		Show the mean redshift for each estimator.}
	}
	\label{fig:pzs-scatter}
	\end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.45\textwidth]{figures/chippr/single_varsigmas_log_estimators.png}
		\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_hivarsig_log_estimators.png}
	\caption{
		The results of \Chippr\ (samples in light blue and optimization in dark blue) and the alternative approaches (the stacked estimator in red and the histogram of modes in yellow) on \pzpdf s with intrinsic scatter of the \lsst\ requirements (left) and twice that (right), with the true redshift density (black curve) and implicit prior (gray curve).
		\Chippr\ is robust to intrinsic scatter, but the alternatives suffer from overly broad \nz\ estimates that worsen with increasing intrinsic scatter.
%		\aim{TODO: Label panels.
%		Show the mean redshift for each estimator.}
	}
	\label{fig:results-scatter}
	\end{center}
\end{figure*}

@@

\begin{figure}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/single_uout-mega_scatter.png}\\
	\includegraphics[width=0.45\textwidth]{figures/chippr/single_uout_log_estimators.png}
	\caption{
		Top: Examples of \pzpdf s with a uniformly distributed catastrophic outlier population at the level of the \lsst\ requirements, including samples from the probability space of true and observed redshift (black points), \pzpdf s (colored step functions), and the true redshifts of the example \pzpdf s (colored vertical lines), with marginal histograms (light gray) for each dimension with the true redshift distribution (black) and implicit prior (dark gray) in the insets.
%		\aim{TODO: Include slice further up.
%		Label panels.}
		Bottom: The results of \Chippr\ (samples in light blue, optimization in dark blue) and the alternative approaches (the stacked estimator in red, the histogram of modes in yellow) on \pzpdf s with uniformly distributed catastrophic outliers, with the true redshift density (black curve) and implicit prior (gray curve).
%		\aim{TODO: Label panels.
%		Show the mean redshift for each estimator.}
		The presence of the catastrophic outlier population broadens the histogram of modes and stacked estimator of the redshift distribution, but the result of \Chippr\ is unbiased.
	}
	\label{fig:uniform-outliers}
	\end{center}
\end{figure}

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_eout-mega_scatter.png}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_rout-mega_scatter.png}
	\caption{
		Examples of \pzpdf s with a catastrophic outlier population like that seen in template-fitting \pzpdf\ codes (left) and machine learning \pzpdf\ codes (right), including samples from the probability space of true and observed redshift (black points), \pzpdf s (colored step functions), and the true redshifts of the example \pzpdf s (colored vertical lines), with marginal histograms (light gray) for each dimension with the true redshift distribution (black) and implicit prior (dark gray) in the insets.
%		\aim{TODO: Label panels.
%		Include slices higher up.}		
	}
	\label{fig:nonuniform-outliers-data}
	\end{center}
\end{figure*}

@@

\begin{figure*}
	\begin{center}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_eout_log_estimators.png}
	\includegraphics[width=0.45\textwidth]{figures/chippr/thesis_rout_log_estimators.png}
	\caption{
		The results of \Chippr\ (samples in light blue and optimization in dark blue) and the alternative approaches (the stacked estimator in red, the histogram of modes in yellow) on \pzpdf s with catastrophic outliers like those seen in template-fitting \pzpdf\ codes (left) and machine learning \pzpdf\ codes (right) to the \lsst\ requirements, with the true redshift density (black curve) and implicit prior (gray curve).
		Though the histogram of modes is most sensitive to a catastrophic outlier population, the stacked estimator also overestimates \nz\ under (machine learning-like outliers) and beyond (template fitting-like outliers).
%		\aim{TODO: Label panels.
%		Show the mean redshift for each estimator.}
	}
	\label{fig:nonuniform-outliers-results}
	\end{center}
\end{figure*}

@@

Systematic bias in \pz\ point estimates, is a concern for \lsst's cosmology results, for the same reasons explored in \citet{hoyle_dark_2018}.
This form of bias is typically summarized by a shift parameter $\Delta_{z} = (\langle \pr{z \gvn \hat{\ndphi}} \rangle - \langle \pr{z \gvn \ndphi^{\dagger}} \rangle)$ representing a difference between the first moment of the estimated redshift density function and that of the true redshift density function.
To distinguish other aforementioned manifestations of bias from this common form of bias, we refer to $\Delta_{z}$ as the \textit{canonical bias}.

@@

%\que{Add back the results of the LSST requirements here?}

@@

@@

@@

%\que{TODO: Break up conclusion into subsections of \Sect{sec:alldata}/\Sect{sec:results}?}

@@

@@

We perform the derivation of \Eq{eqn:fullpost} using log-probabilities.  
What we wish to estimate is then the full log-posterior probability distribution (hereafter the full log-posterior) of the hyperparameters $\ndphi$ given the catalog of photometry $\{\data_{j}\}$.

@@

%\aim{TODO: find way to cite Dance Your Ph.D. video}
